Tampering Detection In Low-Power \\ Smart Cameras

### 2015-06-22 paper.tex
minor edits nell'intro e didascalia 4

%What are the key components of my approach and results? Also include any specific limitations.
We address the detection of camera blurring and displacement (Section \ref{sec:probForm}), and propose an algorithm (Section~\ref{sec:propSol}) that relies on indicators that can be easily computed in low-power smart cameras. We monitor the average image intensity or frame difference (FD) (to detect camera displacement), and the average gradient norm (to detect blurring), and consider any frame yielding an outlier as tampered. In particular, we show that separately monitoring these indicators over different regions of the image can substantially improve the displacement-detection performance. Image regions are defined during an initial configuration phase (Section \ref{subsec:Segmentation}), thus the algorithm operates at a negligible computational overhead w.r.t. monitoring the whole image (Section \ref{subsec:coputationalComplexity}). Our algorithm thus represents a prompt trigger, to be possibly combined with other sequential monitoring techniques. Experiments (Section \ref{sec:experiments}) show that leveraging image regions can substantially improve the displacement-detection performance. % Concluding remarks and discussions are given in Section \ref{sec:Conclusion}.

@@

For each $z_t$, we compute the luma and frame difference separately on each of the $K$ regions,
\begin{eqnarray}
\vspace{-0.5cm}
l_k(t) &=& \frac{1}{\#R_k} \sum_{x \in R_k} z_t(x) \label{eq:lumaRegions}\\
d_k(t) &=&\frac{1}{\#R_k} \sum_{x \in R_k} \left(z_t(x) - z_{t-1}(x) \right)^2, \ \ k = 1, \dots, K\,,\label{eq:FDRegions}
\vspace{-0.5cm}
\end{eqnarray}
where $\#(\cdot)$ denotes the cardinality of a set. We can simultaneously monitor both luma and frame difference, even though computing $d_k$ requires to store the previous frame and this also depends on memory availability of the device. In what follows, including Algorithm~\ref{alg:DISPL}, we consider only the luma $l$, but the same procedures apply to the frame difference $d$ as well. The average gradient norm is instead computed over the whole image
\begin{equation}
\label{eq:normaGradiente}
g(t) = \sum_{x \in X} \left (\sqrt{\left(z_t \circledast f_h\right)^2(x) + \left(z_t \circledast f_v\right)^2(x)}\right),
\end{equation}
where $f_h$ and $f_v$ are the horizontal and vertical derivative filters, respectively, and $\circledast$ denotes the 2d convolution.

@@

We recorded $8$ sequences from webcams monitoring different urban areas, yielding overall $24410$ frames. From each frame we have cropped the central area, removing the 50 top-most and bottom-most rows, and the 50 left-most and right-most columns\footnote{Sequences can be provided upon request.}. We have synthetically introduced $5\%$ of tampered frames: displacements have been simulated by moving the central cropping area of a random shift having magnitude between 20 and 50 rows and coulumns (as in Figure \ref{fig:sequences}(b)). Blurring  (as in Figure \ref{fig:sequences}(a)) was simulated by convolution against a Gaussian kernel, with $1\leq\sigma\leq5$ randomly defined. 
%\gi{Adriano: image sizes? blur kernel std? quanti pixel il displacement?}
%The second dataset was recorded using a Raspberry Pi Model B+ \cite{raspberry} mounting a camera module. 
%Few sequences of the first dataset contain real tampering events  (Figure \ref{fig:indicatori}). 
%In the second dataset, tampering was introduced by moving the device or spraying water on the camera lens.

A typical figure of merit for assessing detection performance is the Receiver-Operating Characteristic (ROC) curve, where each point corresponds to a pair (FPR$_\gamma$, TPR$_\gamma$) defined as
%
\[\text{FPR}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{TPR}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}.\]
%
Here, TP$_\gamma$ represents the number of true positives (tampered frames correctly detected), FP$_\gamma$ of false positives (tampering-free frames detected), TN$_\gamma$ of true negatives (tampering-free frames not detected) and FN$_\gamma$ of false negatives (missed tampered frames), for a given value of $\gamma$. ROC curves have been computed by varying $\gamma_l$, $\gamma_d$ and $\gamma_g$ in a range of values between $0.1$ and $50$. 
\vspace{-0.3cm}
\subsubsection{Discussion}
ROC curves in Figure~\ref{fig:ROC}(a)-(b) and the Area Under the Curve (AUC) values reported in the caption confirm that camera displacements can be better detected by monitoring FD than luma, and that it is convenient to define regions segmenting the scene content. As an example, if we set $\gamma_d = 15.6$, Algorithm~\ref{alg:DISPL} operates at $\text{FPR} = 1\%$ and detects nearly all tampering since $\text{TPR} = 99.92\%$. In contrast, to achieve $\text{FPR} = 1\%$ when monitoring the whole image, FPR drops to $91.67\%$ ($\gamma_d = 6.5$), and when considering Voronoi to $\text{TPR} = 89.05\%$ ($\gamma_d = 18.64$). When monitoring $l$, Algorithm~\ref{alg:DISPL} achieves TPR~=~$73.98\%$ at $\text{FPR}=1\%$  ($\gamma_d=5.8$), while monitoring the whole image is quite ineffective ($\text{TPR} = 17.85\%$, $\gamma_d=3.7$), and similarly perform Voronoi's regions ($\text{FPR} = 53.02\%$, $\gamma_d=6$). We remark that, in the considered low-power scenario, it is important to operate at low FPR, given the large number of frames that smart cameras have to process over time and the cost of data-transmission in terms of battery power. As far as the values of $\Gamma_d$ and $\Gamma_l$ are concerned, the most effective configuration consists in raising an alert as soon as a single region fires a very clear outlier, which implies setting quite wide intervals~\eqref{eq:confidenceRegions}. This option is also preferable because it enables the detection of partial occlusions of the scene.

%\gi{Aggiornare con i nuovi dati}
%\emph{Considering $d$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $0.4\%$ of false alarms, with $\gamma = 24.7$, which is less than one fifth of the whole image solution ($2.2\%$ with $\gamma = 4.6$) and the Voronoi solution ($2.3\%$ with $\gamma = 12.9$).
%On the other side, considering $l$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $13\%$ of false alarms, with $\gamma = 2.5$, which is about one sixth of the whole image solution ($75\%$ with $\gamma = 0.1$) and about three fifty than the Voronoi solution ($22\%$ with $\gamma = 1.7 $).
%Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.} \gi{Aggiornare con i nuovi dati}
Figure~\ref{fig:ROC}(c) confirms that blurring is more effectively detected by monitoring the whole image at once. This is probably due to the fact that, typically, regions do not include the most prominent edge of the scene, which are indeed the most informative parts to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image.%\gi{aggiungere commento su K-1 vornoi che va meglio?}

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{Immagini/curve}
\caption{\textbf{(a)} ROC curves relative to displacement detection based on FD: the AUC obtained by 
``One region - Algorithm 1'' is $99.89\%$, while the AUC obtained by ``Total'' (on the whole 
image) is $99.65\%$.
\textbf{(b)} ROC curves relative to displacement detection based on Luma: the AUC obtained by 
``One region - Algorithm 1'' is $98.44\%$, while the AUC obtained by ``Total'' (on the whole 
image) is $84.07\%$.
\textbf{(c)} ROC curves relative to blurring detection based on Gradient: as opposed to \textbf{(a)} and 
\textbf{(b)}, ``One region - Algorithm 1'' (AUC $98.4\%$) is outperformed by ``Total'' (AUC $99.13\%$).
To highlight differences, the ROC curves in \textbf{(a)} and \textbf{(c)} are drawn over a smaller FPR, TPR range.}
%\caption{\textbf{(a)} ROC curve for displacement detection considering Frame Difference (FD) as indicator.
%	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
%	The AUC corresponding to Algorithm~\ref{alg:DISPL} ($1$ region - Algorithm $1$) is $99.89\%$, while the AUC of considering the whole image (Total) is $99.65\%$. 
%	%the AUC of Luma-Voronoi is $99.85\%$, and the AUC of Frame-Difference is $99.44\%$ (axis have been zoomed for the visualization sake). Large AUC values indicate that these displacements can be successfully detected and that Algorithm~\ref{alg:DISPL} is the most effective one.
%	\textbf{(b)} ROC curve for displacement detection considering Luma as indicator.
%	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
%	The AUC corresponding to Algorithm~\ref{alg:DISPL} ($1$ region - Algorithm $1$) is $98.44\%$, while the AUC of considering the whole image (Total) is $84.07\%$. 
%	\textbf{(c)} ROC curve for blurring detection.
%	In this case, the Gradient-Total (AUC $99.13\%$) outperforms the Gradient-Regions (AUC $98.4\%$) because this latter do not include the most prominent edges in images, which are the most important information to detect blurring. %This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image. 
%	ROC curves \textbf{(a)} and \textbf{(c)}
%	%For the visualization sake, ROC curves \textbf{(a)} and \textbf{(c)} have been reported in a limited range of both axis, and in particular we focus on low values of 1-SPECIFICITY, thus of false alarms.
	%}
\label{fig:ROC}
\end{figure}
%\begin{figure}[htb]
%\centering
%\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus1}}
%\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus_fd}}
%\caption{ROC curves for defocus detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean gradient energy. \textbf{(b)} Analysis of the frame differencing.}
%\label{fig:ROCdisplacement}
%\label{fig:ROCdefocus}
%\end{figure}

>>>>

%What are the key components of my approach and results? Also include any specific limitations.
We address the detection of camera blurring and displacement (Section \ref{sec:probForm}), and propose an algorithm (Section~\ref{sec:propSol}) that relies on indicators that can be easily computed in low-power smart cameras. We monitor the average image intensity or frame difference (to detect camera displacement), and the average gradient norm (to detect blurring), and detect tampered frames by analyzing outliers in these indicators. In particular, we show that separately monitoring these indicators over different regions of the image can substantially improve the displacement-detection performance. Image regions are defined during an initial configuration phase (Section \ref{subsec:Segmentation}), thus the algorithm operates at a negligible computational overhead with respect to monitoring the whole image (Section \ref{subsec:coputationalComplexity}). Our algorithm thus represents a prompt trigger, to be possibly combined with other sequential monitoring techniques. Experiments (Section \ref{sec:experiments}) show that leveraging image regions can substantially improve the displacement-detection performance. % Concluding remarks and discussions are given in Section \ref{sec:Conclusion}.

@@

For each $z_t$, we compute the luma and frame difference (FD) separately on each of the $K$ regions,
\begin{eqnarray}
\vspace{-0.5cm}
l_k(t) &=& \frac{1}{\#R_k} \sum_{x \in R_k} z_t(x) \label{eq:lumaRegions}\\
d_k(t) &=&\frac{1}{\#R_k} \sum_{x \in R_k} \left(z_t(x) - z_{t-1}(x) \right)^2, \ \ k = 1, \dots, K\,,\label{eq:FDRegions}
\vspace{-0.5cm}
\end{eqnarray}
where $\#(\cdot)$ denotes the cardinality of a set. We can simultaneously monitor both luma and frame difference, even though computing $d_k$ requires to store the previous frame and this also depends on memory availability of the device. In what follows, including Algorithm~\ref{alg:DISPL}, we consider only the luma $l$, but the same procedures apply to the frame difference $d$ as well. The average gradient norm is instead computed over the whole image
\begin{equation}
\label{eq:normaGradiente}
g(t) = \sum_{x \in X} \left (\sqrt{\left(z_t \circledast f_h\right)^2(x) + \left(z_t \circledast f_v\right)^2(x)}\right),
\end{equation}
where $f_h$ and $f_v$ are the horizontal and vertical derivative filters, respectively, and $\circledast$ denotes the 2d convolution.

@@

We recorded $8$ sequences from webcams monitoring different urban areas, yielding overall $12200$ frames. From each frame we have cropped the central area, removing the 50 top-most and bottom-most rows, and the 50 left-most and right-most columns\footnote{Sequences can be provided upon request.}. We have synthetically introduced $10\%$ of tampered frames: displacements have been simulated by moving the central cropping area of a random shift having magnitude between 20 and 50 rows and coulumns (as in Figure \ref{fig:sequences}(b)). Blurring  (as in Figure \ref{fig:sequences}(a)) was simulated by convolution against a Gaussian kernel, with $1\leq\sigma\leq5$ randomly defined. 
%\gi{Adriano: image sizes? blur kernel std? quanti pixel il displacement?}
%The second dataset was recorded using a Raspberry Pi Model B+ \cite{raspberry} mounting a camera module. 
%Few sequences of the first dataset contain real tampering events  (Figure \ref{fig:indicatori}). 
%In the second dataset, tampering was introduced by moving the device or spraying water on the camera lens.

A typical figure of merit for assessing detection performance is the Receiver Operating Characteristic (ROC) curve, where each point corresponds to a pair (FPR$_\gamma$, TPR$_\gamma$) defined as
%
\[\text{FPR}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{TPR}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}.\]
%
Here, TP$_\gamma$ represents the number of true positives (tampered frames correctly detected), FP$_\gamma$ of false positives (tampering-free frames detected), TN$_\gamma$ of true negatives (tampering-free frames not detected) and FN$_\gamma$ of false negatives (missed tampered frames), for a given value of $\gamma$. ROC curves have been computed by varying $\gamma_l$, $\gamma_d$ and $\gamma_g$ in a range of values between $0.1$ and $50$. 
\vspace{-0.3cm}
\subsubsection{Discussion}
ROC curves in Figure~\ref{fig:ROC}(a)-(b) and the Area Under the Curve (AUC) values reported in the caption confirm that camera displacements can be better detected by monitoring FD than luma, and that it is convenient to define regions segmenting the scene content. As an example, if we set $\gamma_d = 15.6$, Algorithm~\ref{alg:DISPL} operates at $\text{FPR} = 1\%$ and detects nearly all tampering since $\text{TPR} = 99.92\%$. In contrast, to achieve $\text{FPR} = 1\%$ when monitoring the whole image, FPR drops to $91.67\%$ ($\gamma_d = 6.5$), and when considering Voronoi to $\text{TPR} = 89.05\%$ ($\gamma_d = 18.64$). When monitoring $l$, Algorithm~\ref{alg:DISPL} achieves TPR~=~$73.98\%$ at $\text{FPR}=1\%$  ($\gamma_d=5.8$), while monitoring the whole image is quite ineffective ($\text{TPR} = 17.85\%$, $\gamma_d=3.7$), and similarly perform Voronoi's regions ($\text{FPR} = 53.02\%$, $\gamma_d=6$). We remark that, in the considered low-power scenario, it is important to operate at low FPR, given the large number of frames that smart cameras have to process over time and the cost of data-transmission in terms of battery power. As far as the values of $\Gamma_d$ and $\Gamma_l$ are concerned, the most effective configuration consists in raising an alert as soon as a single region fires a very clear outlier, which implies setting quite wide intervals~\eqref{eq:confidenceRegions}. This option is also preferable because it enables the detection of partial occlusions of the scene.

%\gi{Aggiornare con i nuovi dati}
%\emph{Considering $d$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $0.4\%$ of false alarms, with $\gamma = 24.7$, which is less than one fifth of the whole image solution ($2.2\%$ with $\gamma = 4.6$) and the Voronoi solution ($2.3\%$ with $\gamma = 12.9$).
%On the other side, considering $l$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $13\%$ of false alarms, with $\gamma = 2.5$, which is about one sixth of the whole image solution ($75\%$ with $\gamma = 0.1$) and about three fifty than the Voronoi solution ($22\%$ with $\gamma = 1.7 $).
%Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.} \gi{Aggiornare con i nuovi dati}
Figure~\ref{fig:ROC}(c) confirms that blurring is more effectively detected by monitoring the whole image at once. This is probably due to the fact that, typically, regions do not include the most prominent edge of the scene, which are indeed the most informative parts to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image.%\gi{aggiungere commento su K-1 vornoi che va meglio?}
x
\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{Immagini/curve}
\caption{\textbf{(a)} ROC curves relative to displacement detection based on FD: the AUC obtained by 
``Algorithm 1 - One region'' is $99.89\%$, while the AUC obtained by on the whole 
image is $99.65\%$.
\textbf{(b)} ROC curves relative to displacement detection based on luma: the AUC obtained by 
``Algorithm 1 - One region'' is $98.44\%$, while the AUC obtained on the whole 
image is $84.07\%$.
\textbf{(c)} ROC curves relative to blurring detection based on gradient: as opposed to \textbf{(a)} and 
\textbf{(b)}, ``Algorithm 1 - One region'' (AUC $98.4\%$) is outperformed by monitoring the whole image, AUC = $99.13\%$.
To highlight differences, the ROC curves in \textbf{(a)} and \textbf{(c)} are drawn over a smaller FPR, TPR range.}
%\caption{\textbf{(a)} ROC curve for displacement detection considering Frame Difference (FD) as indicator.
%	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
%	The AUC corresponding to Algorithm~\ref{alg:DISPL} ($1$ region - Algorithm $1$) is $99.89\%$, while the AUC of considering the whole image (Total) is $99.65\%$. 
%	%the AUC of Luma-Voronoi is $99.85\%$, and the AUC of Frame-Difference is $99.44\%$ (axis have been zoomed for the visualization sake). Large AUC values indicate that these displacements can be successfully detected and that Algorithm~\ref{alg:DISPL} is the most effective one.
%	\textbf{(b)} ROC curve for displacement detection considering Luma as indicator.
%	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
%	The AUC corresponding to Algorithm~\ref{alg:DISPL} ($1$ region - Algorithm $1$) is $98.44\%$, while the AUC of considering the whole image (Total) is $84.07\%$. 
%	\textbf{(c)} ROC curve for blurring detection.
%	In this case, the Gradient-Total (AUC $99.13\%$) outperforms the Gradient-Regions (AUC $98.4\%$) because this latter do not include the most prominent edges in images, which are the most important information to detect blurring. %This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image. 
%	ROC curves \textbf{(a)} and \textbf{(c)}
%	%For the visualization sake, ROC curves \textbf{(a)} and \textbf{(c)} have been reported in a limited range of both axis, and in particular we focus on low values of 1-SPECIFICITY, thus of false alarms.
	%}
\label{fig:ROC}
\end{figure}
%\begin{figure}[htb]
%\centering
%\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus1}}
%\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus_fd}}
%\caption{ROC curves for defocus detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean gradient energy. \textbf{(b)} Analysis of the frame differencing.}
%\label{fig:ROCdisplacement}
%\label{fig:ROCdefocus}
%\end{figure}
